\documentclass[12pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

%------------------ Header ------------------%
\section*{Alexander Vysochin}

\textbf{Telegram:} \href{https://t.me/avysochin256}{@avysochin256}\\
\textbf{Email:} \href{mailto:a@vysochin.ru}{a@vysochin.ru} \emph{(preferred method of contact)}\\
\textbf{Location:} Moscow, Russia\\
\textbf{Mobility:} Available for occasional business trips

%------------------ Professional Profile ------------------%
\section*{Professional Profile}
A seasoned DevOps and Cloud-Native Engineer with over 10 years of experience in IT infrastructure design, automation, and cloud technologies. Adept at architecting containerized environments, implementing robust CI/CD pipelines, and developing innovative cloud solutions. Possesses technical leadership and strong problem ownership skills and a proven track record in cross-team collaboration, making complex systems more efficient and scalable.

%------------------ Specializations ------------------%
\section*{Specializations}
\begin{itemize}
    \item DevOps Engineering
    \item Software Development
    \item Systems \& Cloud-Native Engineering
\end{itemize}

%------------------ Employment Preferences ------------------%
\section*{Employment Preferences}
\begin{itemize}
    \item \textbf{Employment Type:} Full Time
    \item \textbf{Work Schedule:} Full day, flexible schedule, remote working
    \item \textbf{Commute:} Preferably within an hour
\end{itemize}

%------------------ Professional Experience ------------------%
\section*{Professional Experience}

\subsection*{Sber – Moscow, Russia}
\textit{Financial Sector – Banking}\\
\textbf{Software Engineer}\\
\textit{November 2023 – Present (1 year 5 months)}
\begin{itemize}
    \item Investigated telemetry storage in ClickHouse.
    \item Explored the implementation of Cilium DSR using tunneling techniques.
    \item Developed a host-based firewall solution for Kubernetes.
    \item Created a supplementary CNI plugin for Kubernetes environments.
    \item Built a diagnostic tool to collect information about Kubernetes clusters and their nodes.
    \item Identified and resolved a packet fragmentation issue in Cilium related to MTU discrepancies.
\end{itemize}
\textbf{Technology Stack:} Linux, XDP, Cilium, Kubernetes, C (\textit{eBPF}), Golang

\subsection*{Nexters Global LTD – Kazakhstan}
\textbf{DevOps Engineer}\\
\textit{November 2022 – November 2023 (1 year 1 month)}
\begin{itemize}
    \item Conducted R\&D and participated in on-call duties and troubleshooting.
    \item Designed and optimized infrastructure architectures.
    \item Facilitated cross-team communication and documented processes for knowledge sharing.
    \item Successfully migrated infrastructure between AWS accounts.
\end{itemize}
\textbf{Technology Stack:} AWS (EC2, EKS, RDS), CI/CD (GitLab, ArgoCD), Helm, Docker, containerd, Terraform, Terragrunt, Atlantis, Golang

\subsection*{MTS (Mobile TeleSystems) – Moscow, Russia}
\textit{IT, System Integration, and Software Development – Telecommunications}\\
\textbf{DevOps Engineer}\\
\textit{August 2021 – October 2022 (1 year 3 months)}
\begin{itemize}
    \item Designed and automated infrastructure solutions.
    \item Managed troubleshooting, release management, and reduction of manual toil.
    \item Built and supported CI/CD pipelines while participating in hiring and onboarding initiatives.
\end{itemize}
\textbf{Technology Stack:} GitLab CI, Terraform, Ansible, SOPS, Helm, Flagger, Fleet, Kubernetes, Istio, Calico, Minio, Golang, Python

\subsection*{VK – Yekaterinburg, Russia}
\textit{IT and Software Development – Internet and Media}\\
\textbf{Private Cloud Installation Team Lead}\\
\textit{March 2021 – July 2021 (5 months)}
\begin{itemize}
    \item Led the private cloud installation team for MCS Private Cloud Installation.
    \item Developed and documented installation tools and projects.
    \item Conducted Scrum meetings and managed team processes, including recruitment and process improvements.
\end{itemize}
\textbf{Technology Stack:} OpenStack

\subsection*{Megafon – Moscow, Russia}
\textit{IT, System Integration, and Software Development – Telecommunications}\\
\textbf{Senior Platform Developer}\\
\textit{February 2019 – February 2021 (2 years 1 month)}
\begin{itemize}
    \item Designed and supported bare-metal Kubernetes clusters and their integrations.
    \item Oversaw IT infrastructure operations, troubleshooting, and team onboarding.
    \item Developed workflows and Helm charts while automating tasks using Terraform and Python.
\end{itemize}

\textbf{Key Technologies:}
\begin{itemize}
    \item Kubernetes, MetalLB, Calico/Flannel, Velero, cert-manager
    \item Rancher, Prometheus, Ceph/RadosGW, Istio, Terraform
    \item Jenkins, GitLab, Artifactory, Grafana, Golang
\end{itemize}

\subsection*{Sima-Land, LLC – Yekaterinburg, Russia}
\textit{IT, System Integration, and Software Development}\\
\textbf{System Engineer}\\
\textit{July 2017 – December 2018 (1 year 6 months)}
\begin{itemize}
    \item Architected and supported corporate cloud services built on KVM/OpenNebula/Ceph, from hardware to web UI.
    \item Designed and maintained a petabyte-scale Ceph cluster and associated network/server hardware.
    \item Built high-availability clusters using Pacemaker, Keepalived, and HAProxy.
    \item Automated tasks using Ansible and Python, managed backup systems (Bareos), and developed monitoring scripts integrated with Zabbix, InfluxDB, and Grafana.
    \item Implemented CI/CD pipelines and developed REST services and parsers using Python (Tornado/Flask).
\end{itemize}

\subsection*{LLP "ASKET" – Petropavlovsk, Russia}
\textbf{System Administrator}\\
\textit{May 2014 – May 2017 (3 years 1 month)}
\begin{itemize}
    \item Configured and managed the BGBilling billing system and administered servers (Debian/Ubuntu).
    \item Managed network hardware from various vendors (D-Link, SNR, ELTEX, BROCADE, UBIQUITY, CISCO).
    \item Maintained software-based BRAS systems (BIRD, Quagga, iproute2, iptables) and monitoring systems (Zabbix, Nagios).
    \item Configured virtualization clusters (Proxmox, KVM, DRBD, Open vSwitch) and automated tasks using Python.
    \item Oversaw DPI system configurations and conducted extensive network and software troubleshooting.
\end{itemize}

%------------------ Education ------------------%
\section*{Education}

\textbf{Bachelor’s Degree}\\
\textit{Siberian State University of Telecommunications and Informatics, Novosibirsk}\\
Year: 2022\\
Major: Information Technology and Communications Systems (Computer Software and Automated Systems)

\vspace{6pt}
\textbf{Petropavl Humanitarian-Technical College}\\
Year: 2014\\
Major: Electronics and Telecommunications (Telecommunications Technician)

%------------------ Professional Development & Certifications ------------------%
\section*{Professional Development \& Certifications}

\begin{itemize}
    \item \textbf{Higher School of Economics, Yekaterinburg} (2021) – Technologies in People Management
    \item \textbf{NPO "Sapphire", Yekaterinburg} (2019) – PostgreSQL 10: Administration, Configuration, Monitoring, and Replication (PostgresPro)
    \item \textbf{FastLane, Saint Petersburg} (2016) – Implementing Cisco MPLS
\end{itemize}

%------------------ Skills ------------------%
\section*{Skills}
\begin{itemize}
    \item \textbf{Cloud Native \& Containerization:} Kubernetes, Docker, OpenStack, Cilium, Containerd, Helm
    \item \textbf{Infrastructure \& Orchestration:} AWS (EC2, EKS, RDS), Bare-metal Kubernetes, Ceph, MetalLB, Istio, Velero, Terraform, Jenkins
    \item \textbf{CI/CD \& Automation:} GitLab CI, ArgoCD, Ansible, Terragrunt, Atlantis
    \item \textbf{Programming \& Scripting:} Golang, Python, C (eBPF)
    \item \textbf{Monitoring \& Observability:} Prometheus, Grafana, Zabbix, InfluxDB
    \item \textbf{Networking \& Security:} Linux, XDP, Calico, Flannel, Firewall Configuration, CNI
    \item \textbf{Methodologies \& Practices:} Agile, Scrum, DevOps, Cross-team Collaboration, R\&D
\end{itemize}

\end{document}
