# Alexander Vysochin

**Telegram:** [@avysochin256](https://t.me/avysochin256)  
**Email:** a@vysochin.ru *(preferred method of contact)*  
**Location:** Moscow, Russia  
**Mobility:** Available for occasional business trips

---

## Professional Profile

A seasoned DevOps and Cloud-Native Engineer with over 10 years of experience in IT infrastructure design, automation, and cloud technologies. Adept at architecting containerized environments, implementing robust CI/CD pipelines, and developing innovative cloud solutions. Possesses technical leadership and strong problem ownership skills and a proven track record in cross-team collaboration, making complex systems more efficient and scalable.

---

## Specializations

- DevOps Engineering
- Software Development
- Systems & Cloud-Native Engineering

---

## Employment Preferences

- **Employment Type:** Full Time  
- **Work Schedule:** Full day, flexible schedule, remote working  
- **Commute:** Preferably within an hour

---

## Professional Experience

### Sber – Moscow, Russia  
*Financial Sector – Banking*  
**Software Engineer**  
*November 2023 – Present (1 year 5 months)*

- Investigated telemetry storage in ClickHouse.
- Explored the implementation of Cilium DSR using tunneling techniques.
- Developed a host-based firewall solution for Kubernetes.
- Created a supplementary CNI plugin for Kubernetes environments.
- Built a diagnostic tool to collect information about Kubernetes clusters and their nodes.
- Identified and resolved a packet fragmentation issue in Cilium related to MTU discrepancies.

**Technology Stack:** Linux, XDP, Cilium, Kubernetes, C (eBPF), Golang

---

### Nexters Global LTD – Kazakhstan  
**DevOps Engineer**  
*November 2022 – November 2023 (1 year 1 month)*

- Conducted R&D and participated in on-call duties and troubleshooting.
- Designed and optimized infrastructure architectures.
- Facilitated cross-team communication and documented processes for knowledge sharing.
- Successfully migrated infrastructure between AWS accounts.

**Technology Stack:** AWS (EC2, EKS, RDS), CI/CD (GitLab, ArgoCD), Helm, Docker, containerd, Terraform, Terragrunt, Atlantis, Golang

---

### MTS (Mobile TeleSystems) – Moscow, Russia  
*IT, System Integration, and Software Development – Telecommunications*  
**DevOps Engineer**  
*August 2021 – October 2022 (1 year 3 months)*

- Designed and automated infrastructure solutions.
- Managed troubleshooting, release management, and reduction of manual toil.
- Built and supported CI/CD pipelines while participating in hiring and onboarding initiatives.

**Technology Stack:** GitLab CI, Terraform, Ansible, SOPS, Helm, Flagger, Fleet, Kubernetes, Istio, Calico, Minio, Golang, Python

---

### VK – Yekaterinburg, Russia  
*IT and Software Development – Internet and Media*  
**Private Cloud Installation Team Lead**  
*March 2021 – July 2021 (5 months)*

- Led the private cloud installation team for MCS Private Cloud Installation.
- Developed and documented installation tools and projects.
- Conducted Scrum meetings and managed team processes, including recruitment and process improvements.

**Technology Stack:** OpenStack

---

### Megafon – Moscow, Russia  
*IT, System Integration, and Software Development – Telecommunications*  
**Senior Platform Developer**  
*February 2019 – February 2021 (2 years 1 month)*

- Designed and supported bare-metal Kubernetes clusters and their integrations.
- Oversaw IT infrastructure operations, troubleshooting, and team onboarding.
- Developed workflows and Helm charts while automating tasks using Terraform and Python.

**Key Technologies:**

|   |   |   |   |   |   |   |   |   |
|---|---|---|---|---|---|---|---|---|
| Kubernetes    || MetalLB || Calico/Flannel || Velero || cert-manager |
| Rancher || Prometheus || Ceph/RadosGW || Istio || Terraform ||
| Jenkins || GitLab || Artifactory || Grafana || Golang ||

---

### Sima-Land, LLC – Yekaterinburg, Russia  
*IT, System Integration, and Software Development*  
**System Engineer**  
*July 2017 – December 2018 (1 year 6 months)*

- Architected and supported corporate cloud services built on KVM/OpenNebula/Ceph, from hardware to web UI.
- Designed and maintained a petabyte-scale Ceph cluster and associated network/server hardware.
- Built high-availability clusters using Pacemaker, Keepalived, and HAProxy.
- Automated tasks using Ansible and Python, managed backup systems (Bareos), and developed monitoring scripts integrated with Zabbix, InfluxDB, and Grafana.
- Implemented CI/CD pipelines and developed REST services and parsers using Python (Tornado/Flask).

---

### LLP "ASKET" – Petropavlovsk, Russia  
**System Administrator**  
*May 2014 – May 2017 (3 years 1 month)*

- Configured and managed the BGBilling billing system and administered servers (Debian/Ubuntu).
- Managed network hardware from various vendors (D-Link, SNR, ELTEX, BROCADE, UBIQUITY, CISCO).
- Maintained software-based BRAS systems (BIRD, Quagga, iproute2, iptables) and monitoring systems (Zabbix, Nagios).
- Configured virtualization clusters (Proxmox, KVM, DRBD, Open vSwitch) and automated tasks using Python.
- Oversaw DPI system configurations and conducted extensive network and software troubleshooting.

---

## Education

**Bachelor’s Degree**  
*Siberian State University of Telecommunications and Informatics, Novosibirsk*  
- **Year:** 2022  
- **Major:** Information Technology and Communications Systems (Computer Software and Automated Systems)

**Petropavl Humanitarian-Technical College**  
- **Year:** 2014  
- **Major:** Electronics and Telecommunications (Telecommunications Technician)

---

## Professional Development & Certifications

- **Higher School of Economics, Yekaterinburg**  
  *2021 – Technologies in People Management*

- **NPO "Sapphire", Yekaterinburg**  
  *2019 – PostgreSQL 10: Administration, Configuration, Monitoring, and Replication (PostgresPro)*

- **FastLane, Saint Petersburg**  
  *2016 – Implementing Cisco MPLS*

---

## Skills

- **Cloud Native & Containerization:** Kubernetes, Docker, OpenStack, Cilium, Containerd, Helm  
- **Infrastructure & Orchestration:** AWS (EC2, EKS, RDS), Bare-metal Kubernetes, Ceph, MetalLB, Istio, Velero, Terraform, Jenkins  
- **CI/CD & Automation:** GitLab CI, ArgoCD, Ansible, Terragrunt, Atlantis  
- **Programming & Scripting:** Golang, Python, C (eBPF)  
- **Monitoring & Observability:** Prometheus, Grafana, Zabbix, InfluxDB  
- **Networking & Security:** Linux, XDP, Calico, Flannel, Firewall Configuration, CNI  
- **Methodologies & Practices:** Agile, Scrum, DevOps, Cross-team Collaboration, R&D
